\documentclass[a4paper,10pt]{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
\usepackage{longtable}

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = Fontin-Bold.otf,
ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

%WATERMARK TEST [**not part of a CV**]---------------
%\font\wm=''Baskerville:color=787878'' at 8pt
%\font\wmweb=''Baskerville:color=FF1493'' at 8pt
%{\wm 
%	\begin{textblock}{1}(0,0)
%		\rotatebox{-90}{\parbox{500mm}{
%			Typeset by Alessandro Plasmati with \XeTeX\  \today\ for 
%			{\wmweb \href{http://www.aleplasmati.comuv.com}{aleplasmati.comuv.com}}
%		}
%	}
%	\end{textblock}
%}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{\Huge Ally \textsc{Weir}
	}\bigskip\par}

%--------------------SECTIONS-----------------------------------
%Section: Personal Data
\section{Personal Data}

\begin{tabular}{rl}
    \textsc{Address:}   & 62 Amochrie Rd, Paisley, PA2 0AH \\
    \textsc{Phone:}     & +447964698129\\
    \textsc{email:}     & \href{mailto:ally.pcgf+grad@gmail.com}{ally.pcgf@gmail.com} \\
    \textsc{GitHub}     & \href{http://www.github.com/allyjweir}{github.com/allyjweir}
\end{tabular}

%Section:Profile
\section{Profile}
I am an enthusiastic Honours Computer Science student in my final year at the University of Glasgow. Throughout my degree and professional experience, I always work to find meaningful solutions to people's problems by leveraging technology. My motivation lies in creating elegent applications that allow people to be more productive and enjoy what they're doing. With a broad skill set, my passion for the subject particularly lies in the areas of human centric computing and mobile convergence.

%Section: Technical Skills
\section{Technical Skills}
Please see my \hyperlink{https://github.com/allyjweir}{GitHub}  profile for extensive examples of my work.
\bigskip\\
\begin{tabular}{r|p{11cm}}
Basic & AngularJS, (Literate) Coffeescript, d3, Bamboo, JUnit, LaTeX \\
Intermediate & Django, Javascript, JQuery, AJAX, LESS, CSS, HTML5, PHP, CodeIgniter, PostgreSQL, MySQL, JIRA, Vagrant   \\
Advanced & Git DSCM, GNU/Linux, Python, Java, Android Development, Windows
\end{tabular}

%Section: Industry Experience
\section{Industry Experience}
\begin{longtable}{r|p{11cm}}
\emph{2014} & ScotlandIS \\&\emph{e-Placement Scotland Placement of the Year}\\&\footnotesize{Awarded at the annual the ICT trade body's annual awards evening, this award represented outstanding work contributed within a student industry placement. This was awarded for my work at the SIMUL8 Corporation. Quoting Nicola Hamil-Phillips of SIMUL8,  \begin{quote}
“Ally is not an intern that makes tea; he is a contributor that has a huge impact on our business and is the driving force behind his projects. We work in a fast paced agile environment and it’s important for us to have people in our company with the skills to make the business successful, Ally is one of those people. He has made a vast contribution to not only the team but also to the company.”
\end{quote}

}\\\multicolumn{2}{c}{}\\
\emph {Summer 2014} & SIMUL8 Corporation \\&\emph{Software Development Intern}\\&\footnotesize{Working as a integral part of a small, agile team my inter-disciplinary work included developing new features from inception to deployment and improving existing systems. I also implemented a number of new development practices used in the team such as continual integration and deployment as well as a Vagrant based standardised workspace with the aim of simplifying workflows. This spanned numerous languages and tools including PHP 5.5 and the CodeIgniter framework. All the work I contributed was valuable to the core business aims while developing my personal skillset extensively.}\\\multicolumn{2}{c}{}\\
\end{longtable}

\clearpage

%Section: Projects
\section{Technical Projects}
\begin{longtable}{r|p{12cm}}
\emph {2014-15} & Lackawanna \\&\emph{Sole Developer}\\&\footnotesize{My final year Honours project, Lackawanna is a Qualitative Data Analysis Cloud Platform. In early stages of its development, the project aims to streamline and simplify researcher's workflow when cataloging, organising and leveraging qualitative data such as audio, video and PDFs.}\\\multicolumn{2}{c}{} \\
\emph {2013-14} & Wanders \\&\emph{Team Leader}\\&\footnotesize{With the aim to construct an interactive soundscape of a city, this multi-disciplinary project incorporated an Android application to collect ambient information of a user's surroundings. This was stored in a Django application where users could explore and combine recordings as they explored a city. I touched all aspects of the project as the Scrum Master, lead designer, sole Android developer and Django developer.}\\\multicolumn{2}{c}{} \\
\emph {2014} & Aggressive Backpack - Collaborative Requirements Tracker \\&\emph{System Architect, Designer}\\&\footnotesize{3 month distributed information systems project in the Django framework to create a collaborative workspace for asyncronous development teams. My focus was on the UI/UX while also constructing the backend.}\\\multicolumn{2}{c}{} \\
\emph {2013} & World Standings \\&\emph{Data Engineer, Developer}\\&\footnotesize{This short project focused on using data from the World Health Organisation and the 2012 Olympic Games, to find meaningful connections in the datasets. We leveraged the d3 JavaScript library to create an imaginative range of visualisations in a constrained timescale. }\\\multicolumn{2}{c}{} \\
\end{longtable}


%Section: Work Experience
\section{Work Experience}
\begin{longtable}{r|p{11cm}}
 \emph{Sept 2014} & Software Development Intern \\\textsc{June 2014}&\emph{SIMUL8 Corporation}\\&\footnotesize{See industry experience above.}\\\multicolumn{2}{c}{} \\
 \emph{Current} & Manager \\\textsc{Apr 2013}&\emph{The Bield Climbing Wall}\\&\footnotesize{I am part of a Scout team that recently developed this small, independent climbing wall. It is quickly evolving into a local resource for numerous youth groups and schools. I develop new routes on the walls, run sessions and maintain equipment while managing bookings and the related admin work. My skills in communication and management are key when working with our distributed network of users and instructors.}\\\multicolumn{2}{c}{} \\
 \emph{Oct 2012} & Specialist \\\textsc{Aug 2011}&\emph{Apple Store Braehead, Glasgow}\\&\footnotesize{I joined Apple for the opening of the Braehead, Glasgow store. Working as a Specialist I directly assisted customers with their purchases, using my extensive knowledge and enthusiasm for technology to find what they were looking for and troubleshoot issues with their devices. These skills made me a "go-to" for technical knowledge and advice amongst my co-workers. My passion for meaningful interactions with customers and attention to detail was enhanced, contributing to my store's position in the top 25 performing Apple stores worldwide for customer service.}\\\multicolumn{2}{c}{} \\
\pagebreak\emph{Jul 2011} & IFS Co-worker \\\textsc{Oct 2010}&\emph{IKEA Glasgow}\\&\footnotesize{Working for the world's largest producer of furniture gave me a keen insight to the workings of a multinational company and the organisation required to run such an undertaking. I worked in the Glasgow store’s restaurant. My responsibilities were to maintain a high hygiene standard while assisting customers in a helpful, friendly manner. This gave me a strong work ethic and instilled an ‘if you’re going to do something, do it right’ mentality.}\\\multicolumn{2}{c}{} \\
\end{longtable}

%Section: Education
\section{Education}
\begin{tabular}{r|p{11cm}}
 \emph{Current} & 4th year of Undergraduate Degree - BSc (Hons) Computer Science \\\textsc{Sept 2011}&\emph{University of Glasgow}\\&\footnotesize{ \begin{itemize}
 \item \textbf{On track for 2:1}
 \item \textbf{Final Year Project} | Qualitative Data Analysis Cloud Platform |  \textit{ Advisor: Karen Renaud}
 \item \textbf{Penultimate Year Project} | Multi-device Recording System | \textit{Advisor: Prof. John Williamson}
 \item Studied English Literature for 2 years previously
 \end{itemize}}\\\multicolumn{2}{c}{} \\
 \emph{2011} & Student \\\textsc{2005}&\emph{Gleniffer High School}\\&\footnotesize{Advanced Higher at A 
            \begin{itemize}
                \item English (Band 1)
            \end{itemize}
    \par Highers at A 
            \begin{itemize}
                \item English, Maths, Computing, Physics (All Band 1)
            \end{itemize}
    \par Highers at B
            \begin{itemize}
                \item Chemistry
            \end{itemize}}\\
    \multicolumn{2}{c}{} \\

\end{tabular}


%Section:Voluntary
\section{Voluntary Work}
\begin{longtable}{r|p{11cm}}
\emph{Current} & Class Representative \\\textsc{Sept 2014}&\emph{4th Year Computer Science, University of Glasgow}\\&\footnotesize{As class representative I serve as the bridge between faculty and the student corpus. By gathering positive and negative feedback related to the class's learning experience, I create solutions and mediate issues to improve the learning experience for myself and fellow peers.}\\\multicolumn{2}{c}{} \\
\emph{Current} & Scout Leader \\\textsc{Jan 2010}&\emph{2nd Paisley Abbey Scouts}\\&\footnotesize{I have worked consistently as part of the Scout section's leadership team to offer a varied programme throughout the year. While improving my communication skills and teamworking with other leaders, I have also furthered my leadership abilities running activities for the Scouts themselves.\par I have organised trips to National Activity Centres and taught numerous outdoor skills such as bushcraft and backwoods cooking. These have improved my organisational skills while allowing me to foster each Scout's own skills in outdoorsmapship and teamwork.}\\\multicolumn{2}{c}{} \\
\pagebreak\emph{Current} & Quartermaster \\\textsc{Jan 2010}&\emph{2nd Paisley Abbey Scouts}\\&\footnotesize{My responsibilities in this role involve organising and cataloging all the equipment used by my Scout group. In this role I make use of keen insight into the organisation and ongoing communication with teams to facilitate their programmes. I also carry out maintainance and purchase new equipment based on feedback and keeping track of what is needed.}\\\multicolumn{2}{c}{} \\
\emph{Jan 2009} & Volunteer, \\\textsc{Dec 2009}&\emph{Erskine Hospital}\\&\footnotesize{While volunteering at Erskine Hospital I took part in numerous roles to improve the quality of life for the ex-servicemen and women in residence. These included groundskeeping, entertainment, fundraising and administration work. These helped improve my teamwork particularly working with those from completely different walks of life.}
\end{longtable}

%Section: Interests
\section{Interests and Activities}
\begin{tabular}{r|p{11cm}}
Technology & Increasing productivity, APIs, UI/UX\\
Sports & Rock Climbing, Hillwalking, Road Cycling\\
Other & Scouting, Travelling, Literature
\end{tabular}

\end{document}
